\documentclass[paper=a4,fontsize=11pt]{scrartcl} % KOMA-article class
              
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{amsmath,amsfonts,amsthm}     % Math packages
\usepackage{graphicx}                    % Enable pdflatex
\usepackage[svgnames]{xcolor}            % Colors by their 'svgnames'
\usepackage{geometry}
  \textheight=700px                    % Saving trees ;-)
\usepackage{url}

\frenchspacing              % Better looking spacings after periods
\pagestyle{empty}           % No pagenumbers/headers/footers


%%% ------------------------------------------------------------
\usepackage{sectsty}

\sectionfont{%                  % Change font of \section command
  \usefont{OT1}{phv}{b}{n}%    % bch-b-n: CharterBT-Bold font
  \sectionrule{0pt}{0pt}{-5pt}{3pt}}

%%% Macros
\newlength{\spacebox}
\settowidth{\spacebox}{8888888888}      % Box to align text
\newcommand{\sepspace}{\vspace*{1em}}    % Vertical space macro

\newcommand{\MyName}[1]{ % Name
    \Huge \usefont{OT1}{phv}{b}{n} \hfill #1
    \par \normalsize \normalfont}
    
\newcommand{\MySlogan}[1]{ % Slogan (optional)
    \large \usefont{OT1}{phv}{m}{n}\hfill \textit{#1}
    \par \normalsize \normalfont}

\newcommand{\NewPart}[1]{\section*{\uppercase{#1}}}

\newcommand{\PersonalEntry}[2]{
    \noindent\hangindent=2em\hangafter=0 % Indentation
    \parbox{\spacebox}{        % Box to align text
    \textit{#1}}           % Entry name (birth, address, etc.)
    \hspace{1.5em} #2 \par}    % Entry value

\newcommand{\SkillsEntry}[2]{      
    \noindent \textbf{#1} \hfill                          % items
    \noindent\hangindent=2em\hangafter=0 \small #2 \par   % skills
    \normalsize \par}
    
\newcommand{\EducationEntryMaster}[3]{
    \noindent \textbf{#1} \hfill      % Study
    #2 \par  % Duration
    \noindent \textit{#3} \par        % School
    \normalsize \par}
        
\newcommand{\EducationEntryBachler}[4]{
    \noindent \textbf{#1} \hfill      % Study
    #2 \par  % Duration
    \noindent \textit{#3} \par        % School 1
        \noindent \textit{#4} \par        % School 2
    \normalsize \par}

%%% Begin Document
\begin{document}
\MyName{Wang Yang}
\MySlogan{Target: Software Engineer}
\sepspace

%%% Personal details
\NewPart{Personal details}{}
\PersonalEntry{Phone}{(+86) 13552133119}
\PersonalEntry{Mail}{\url{khil.wang@gmail.com}}

%%% Education
\NewPart{Education}{}
\EducationEntryMaster{MSc. Computer Science}{2009-2012}{Chinese Academy of Science Software Institude}
\sepspace
\EducationEntryBachler{BSc. Telecommunication Engineering}{2005-2009}{Queen Mary, University of London} {Beijing University of Posts Telecommunications}

%%% Work experience
\NewPart{Work experience}{}
                     
\noindent \textbf{Senior Software Engineer, Tencent} \hfill
2012-present \par 
\noindent \textit{1. Online Advertising Training System.} 
{2015.1-now} \par 
\noindent\hangindent=2em\hangafter=0 \small 
{I developed a distributed model training system. The model is used to predict Click Through Rate(CTR) of Advertisement. The system is based on Storm/Kafka-like infrastructure. The training data is generated via click/impression log and join with user/ads/context features(stored in distributed KV), then feed into one-pass(online) algorithm(FTRL) and periodically dump the model for serving. In order to equally placed the memory consumed component I designed custom scheduler of storm.} \par 
\noindent \textit{2. Training Data Generation System.} 
{2013.1-2014.12} \par 
\noindent\hangindent=2em\hangafter=0 \small 
{The click/impression log first fill into distributed queuing system(Kafka-like), then divided into different Ad position and extract keys to join with user/ads/context features, and finally dump training data into HDFS for offline model training purpose. I use 32*8 CPU to handle 15 Billions impression for each cluster set(I have 2 set, one for production, another for experiment)} \par 
\noindent \textit{3. Online Training Monitor} 
{2015.1-2015.5} \par 
\noindent\hangindent=2em\hangafter=0 \small 
{I developed plenty of metric for monitoring task, for the model specific: Delay AUC, Real-time AUC, Loss, Miss-classification-rate, model-size; for the system specific: memory-used, batch-process-time. This project initially base on Graphite. Then I expanded the monitoring system to include metric from Training Data Generation System and Online Advertising Training System and migrated it into another more featured monitoring system(dev by another team).} \par
\noindent \textit{4. Distributed Database Engine Optimizer} 
{2012.6 - 2013.1} \par 
\noindent\hangindent=2em\hangafter=0 \small 
{I developed Bool Expression Analyzer which is the fundamental component of Optimizer in SQL compiler. I implemented the Quine McCluskey algorithm to generate conjunctive normal form(CNF) and use Petrick Method to get Minimal-CNF. Based on the bool expression analyzer, I developed Predicate Push-down Optimizer for logical plan. And I also developed Reduce Shuffling Optimizer for physical plan.} \par


%%% Skills
\NewPart{Skills}{}
\SkillsEntry{Languages}{Java, Python, C++, Unix-like (*nix) Shell}
\SkillsEntry{Knowledge}{Data structure and Algorithm, Machine Learning, Distributed System}

\end{document}

